---
title: "Linear Model with Prediction"
author: "Destiny Calvillo"
date: "7/6/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tigerstats)
library(tidyverse)
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)
```

## Including Plots

You can also embed plots, for example:


Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

###Plot scatterplot

```{r}
plot(SIMS~ARM,data=data)
```

##Now with ggplot - first select the basic data

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```
##Now add in scatterplot

```{r}
basicNN + geom_point()
```

The Y-axis is SIMS and the X-axis is ARM. This plot shows that there is a positive linear correlation. 

# Numerical results

```{r}
cor(SIMS~ARM,data=data)
```

Above is the value of correlation, the value is 0.68. Since the value is a positive number, we should expect the sea of points to go uphill towards the right. We can also verify this in the scatter-plots from earlier. 

# Inferential  (Build linear model)
  
```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

The equation for the line that fits this is SIMS= -4.1 + 0.05 * R. The formula needed is y= mx + b to create the corresponding line. The Adjusted R-squared is the number to look at. 

# now add the model fit to our plot
  
```{r}
basicNN + geom_point( ) + geom_smooth(method=lm)
``` 

It appears that the value of the Y-intercept would be around 1. 
