---
title: "Linear Model with Prediction"
author: "Destiny Calvillo"
date: "7/6/2021"
output: 
  html_document:
    toc: true
    toc_depth: 5
  

---

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(knitr)
```
# SIMS ~ ARM
## Plot of SIMS~ARM
## Numerical Summary
## Inferential Results
## Plot with fitted line
# SIMS ~ GRIP
## Plot of SIMS~GRIP
## Numerical Summary
## Inferential Results
## Plot with fitted line
# SIMS ~ ARM + GRIP
## Inferential Results
# Comparing Models
## Assessing SIMS~ARM how good is it
### Comparing SIMS~ARM to SIMS~GRIP
### Comparing SIMS~ARM to SIMS~ARM+GRIP 
#### Statistical test of SIMS~ARM to SIMS~ARM+GRIP 


# SIMS ~ ARM
## Plot of SIMS~ARM
```{r}
plot(SIMS~ARM,data=basicNN)
```
```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```
```{r}
basicNN + geom_point()
```

The Y-axis is SIMS and the X-axis is ARM. This plot shows that there is a positive linear correlation. 

## Numerical Summary

```{r}
cor(SIMS~ARM,data=data)
```

Above is the value of correlation, the value is 0.68. Since the value is a positive number, we should expect the sea of points to go uphill towards the right. We can also verify this in the scatter-plots from earlier. 

## Inferential Results
  
```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

The equation for the line that fits this is SIMS= -4.1 + 0.05 * R. The formula needed is y= mx + b to create the corresponding line. The Adjusted R-squared is the number to look at. 

## Plot with fitted line
  
```{r}
basicNN + geom_point( ) + geom_smooth(method=lm)
``` 

It appears that the value of the Y-intercept would be around 1. 
